---
title: "Oct31"
author: "Julie Jung"
date: "October 31, 2017"
output: html_document
---
Zombie dataset – 
-  pull out all the indivs that are medical/nursing majors
-	what is the relationship in those indivs:
o	–between age and years of education
o	with years of education used as a continuous variable. 
-	Also plot as a scatterplot with
o	Appropriate regression line
o	With 95% CI
o	Color the points so that males are pink and females are blue. 

```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

-  pull out all the indivs that are medical/nursing majors
```{r}
medicalmajors <- subset(d, major == "medicine/nursing", na.rm=T)
```

-  what is the relationship in those indivs:
      o	–between age and years of education
      o	with years of education used as a continuous variable. 

```{r}
m <- lm(data = medicalmajors, years_of_education ~ age)
hist(m$residuals)
library(car)
qqPlot(m$residuals)
s <- shapiro.test(m$residuals)
s  #non-normal

#another way to check if normal
hist(medicalmajors$years_of_education) #non-normal

#take out zeros
non0medicalmajors <- subset(medicalmajors, years_of_education > 0)
hist(log(non0medicalmajors$years_of_education))
qqnorm(log(non0medicalmajors$years_of_education)) #non normal
shapiro.test(log(non0medicalmajors$years_of_education)) # non normal
```
The data are non-normal, so we need to use a non-parametric test. 

```{r}
cor(medicalmajors$age, medicalmajors$years_of_education, method = "kendall")
```
This test indicates that the correlation between age and years of education is quite low, 0.1637. 

NEXT PART: 

-  Also plot as a scatterplot with
      o	Appropriate regression line
      o	With 95% CI
      o	Color the points so that males are pink and females are blue. 

```{r}
library(ggplot2)

males <- subset(medicalmajors, gender == "Male")
females <- subset(medicalmajors, gender == "Female")

ggplot(medicalmajors, aes(x=age, y=years_of_education, color=gender)) + 
  geom_point(data=males, size=4, color="Pink") +
  geom_smooth(data=males, method=lm, color="Pink") +
  geom_point(data=females, size=4, color="Blue") +
  geom_smooth(data=females, method=lm, color="Blue") +
  ylab("Years of education\n")+
  theme_bw(20) +
  xlab("Age (years)")

```